Towards Explainability of Machine Learning Models in Insurance Pricing

### 2020-03-05 manuscript/manuscript.Rmd
redactions

---
title: Towards Explainability of Machine Learning Models in Insurance Pricing
author:
  - name: Kevin Kuo
    email: kevin@kasa.ai
    affiliation: a
    footnote: Corresponding Author
  - name: Daniel Lupton
    email: dlupton@taylorandmulder.com
    affiliation: b
address:
  - code: a
    address: Kasa AI, 3040 78th Ave SE \#1271, Mercer Island, WA 98040, USA
  - code: b
    address: Taylor & Mulder, 10508 Rivers Bend Lane, Potomac, MD 20854, USA
abstract: |
  Machine learning methods have garnered increasing interest among actuaries in
  recent years. However, their adoption by practitioners has been limited, partly
  due to the lack of transparency of these methods, as compared to generalized 
  linear models. In this paper, we discuss the need for model interpretability in
  property & casualty insurance ratemaking, propose a framework for explaining 
  models, and present a case study to illustrate the framework.

@@

Acknowledgments {.unnumbered}
==========

We thank Navdeep Gill, Daniel Falbel, Morgan Bugbee, the volunteers of the CAS
project oversight group, and two anonymous reviewers for helpful discussions
and/or feedback.
This work is supported by the Casualty Actuarial Society.

@@

[^1]: https://github.com/kasaai/explain-ml-pricing

>>>>

---
title: Towards Explainability of Machine Learning Models in Insurance Pricing
author:
  - name: (redacted)
    email: (redacted)
    affiliation: a
    footnote: Corresponding Author
  - name: (redacted)
    email: (redacted)
    affiliation: b
address:
  - code: a
    address: (redacted)
  - code: b
    address: (redacted)
abstract: |
  Machine learning methods have garnered increasing interest among actuaries in
  recent years. However, their adoption by practitioners has been limited, partly
  due to the lack of transparency of these methods, as compared to generalized 
  linear models. In this paper, we discuss the need for model interpretability in
  property & casualty insurance ratemaking, propose a framework for explaining 
  models, and present a case study to illustrate the framework.

@@

@@

[^1]: (redacted)
